---
title: "Project Euler"
author: "H. Cole Warren"
date: December 22, 2018
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Multiples of 3 and 5
### Problem 1

If we list all the natural numbers below 10 that are multiples of 3 or 5, we get 3, 5, 6 and 9. The sum of these multiples is 23.

Find the sum of all the multiples of 3 or 5 below 1000.

```{r p1}
number_line <- 1:1000

logical_vector <- number_line %% 3 || number_line %% 5

sum(number_line[logical_vector])
```

## Even Fibonacci numbers
### Problem 2

Each new term in the Fibonacci sequence is generated by adding the previous two terms. By starting with 1 and 2, the first 10 terms will be:

$$ 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, ... $$

By considering the terms in the Fibonacci sequence whose values do not exceed four million, find the sum of the even-valued terms.

```{r p2}
# Create a function that generates the first n terms of the fibonacci sequence
fib <- function(n = 20) {
  output <- vector("integer", n) # Preallocate the entire vector
  output[1:2] <- c(1, 1)
  for (i in 3:n) output[i] <- output[i-1] + output[i-2]
  output
}

# The 34th term is the first term greater than 4 million
fib_seq <- fib(n = 33)

logi_vec <- as.logical(fib_seq %% 2)

sum(fib_seq[logi_vec])
```

## Largest prime factor
### Problem 3

The prime factors of 13195 are 5, 7, 13 and 29.

What is the largest prime factor of the number 600851475143 ?

```{r p3}
# First generate a sequence if prime numbers

# Check primes between the first prime number and half the number in question (inclusive) to see if they will divide the number

# 
```

## Largest palindrome product
### Problem 4

A palindromic number reads the same both ways. The largest palindrome made from the product of two 2-digit numbers is 9009 = 91 × 99.

Find the largest palindrome made from the product of two 3-digit numbers.

```{r p4}

```

## Smallest multiple
### Problem 5

2520 is the smallest number that can be divided by each of the numbers from 1 to 10 without any remainder.

What is the smallest positive number that is evenly divisible by all of the numbers from 1 to 20?

```{r p5}

```

## Sum square difference
### Problem 6

The sum of the squares of the first ten natural numbers is,

$$ 12 + 22 + ... + 102 = 385 $$

The square of the sum of the first ten natural numbers is,

$$ (1 + 2 + ... + 10)2 = 552 = 3025 $$

Hence the difference between the sum of the squares of the first ten natural numbers and the square of the sum is 3025 - 385 = 2640.

Find the difference between the sum of the squares of the first one hundred natural numbers and the square of the sum.

```{r p6}

```
